Exponential Integrals\\ [1ex]

### 2022-02-11 draft2.tex
Confirm the 3/2-derivative formula in the Airy case?
I think the calculation works now, though it still needs double-
checking. I'm doubtful about the constant factor.

Let us study the RHS of claim \eqref{claim 2}. \textbf{Note that} $x = \tfrac{1}{2} + \tfrac{3}{4} \zeta$ and $y = \tfrac{1}{2} + \tfrac{3}{4} s$

@@

&\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds=2\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}s\,\,{}_2F_1\left(\frac{4}{3},\frac{5}{3};\frac{3}{2};\frac{9}{4}s^2\right)ds & \\

@@

&=-\frac{4}{9\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-y\right)-{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};y\right)\right]dy & x\in (-\infty,0) \\
&=\frac{4}{9\sqrt{3}} \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \int_0^x(x-y)^{-1/2}\left[ e^{-(1/3) \pi i} \frac{e^{(5/3) \pi i} y^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} + e^{-(2/3) \pi i} \frac{e^{(7/3) \pi i} y^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\
&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \int_0^x(x-y)^{-1/2}\left[ e^{(4/3) \pi i} \frac{y^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} + e^{(5/3) \pi i} \frac{y^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\

@@

&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \left[ e^{(4/3) \pi i} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{3})} \frac{x^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \textcolor{red}{+} e^{(5/3) \pi i} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3})} \frac{x^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right] & \eqref{4.8} \\
&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ e^{(4/3) \pi i} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} x^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right) + e^{(5/3) \pi i} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} x^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right) \right] & \eqref{4.8} \\
&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ e^{(4/3) \pi i} e^{-(7/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(2) \Gamma(\tfrac{1}{6})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{6})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right. \\
& \qquad\qquad\qquad\qquad + \left. e^{(5/3) \pi i} e^{-(11/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(2) \Gamma(\tfrac{5}{6})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ e^{(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ e^{(1/3) \pi i} e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{(2/3) \pi i} e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ \tfrac{1}{2} \left( e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) - e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right) \right. \\
& \qquad\qquad\qquad\qquad \left. + i\tfrac{\sqrt{3}}{2} \left( e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right) \right] \\
&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ \tfrac{1}{2} \big(e^{(7/6) \pi i} - e^{(11/6) \pi i}\big)\,w_3(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right. \\
& \qquad\qquad\qquad\qquad \left. - i\tfrac{\sqrt{3}}{2} \left( e^{-(7/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} \frac{\Gamma(\tfrac{5}{6}) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{2}{3}) \Gamma(\tfrac{5}{6})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{-(11/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{1}{6}) \Gamma(-\tfrac{2}{3})}{\Gamma(-\tfrac{2}{3}) \Gamma(\tfrac{1}{6})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right) \right] \\
&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ \tfrac{1}{2} \big(e^{(7/6) \pi i} - e^{(11/6) \pi i}\big)\,w_3(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right. \\
& \qquad\qquad\qquad\qquad \left. - i\tfrac{\sqrt{3}}{2} \left( e^{-(7/6) \pi i} \frac{\Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} \frac{\sin(\tfrac{1}{3}\pi)}{\sin(\tfrac{1}{6}\pi)} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{-(11/6) \pi i} \frac{\Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} \frac{\sin(-\tfrac{2}{3}\pi)}{\sin(\tfrac{1}{6}\pi)} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right) \right] \\

@@

however, ${}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}+\frac{\zeta}{4}\right)$ has a branch cut at $\zeta\in(2/3,+\infty)$, thus the claim holds true.

>>>>

Let us study the RHS of claim \eqref{claim 2}. \textbf{Note that $x = \tfrac{1}{2} - \tfrac{3}{4} \zeta$ and $y = \tfrac{1}{2} - \tfrac{3}{4} s$.

@@

&\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds \\
&= 2\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}s\,\,{}_2F_1\left(\frac{4}{3},\frac{5}{3};\frac{3}{2};\frac{9}{4}s^2\right)ds & \\

@@

&=\frac{4}{9\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};y\right)-{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-y\right)\right]dy & x\in (-\infty,0) \\
&=\frac{4}{9\sqrt{3}} \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \int_0^x(x-y)^{-1/2}\left[ e^{-(1/3) \pi i} \frac{e^{(5/3) \pi i} y^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right. \\
& \qquad\qquad\qquad\qquad\qquad\qquad\qquad \left. + e^{-(2/3) \pi i} \frac{e^{(7/3) \pi i} y^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0)
Continue $w_5$ and $w_6$ clockwise around their singularities at zero.}
&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \int_0^x(x-y)^{-1/2}\left[ e^{-(1/3) \pi i} \frac{|y|^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right. \\
& \qquad\qquad\qquad\qquad\qquad\qquad \left. + e^{-(2/3) \pi i} \frac{|y|^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\

@@

&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \left[ e^{-(1/3) \pi i} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{3})} \frac{|x|^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right. \\
& \qquad\qquad\qquad\qquad \left. + e^{-(2/3) \pi i} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3})} \frac{|x|^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right] & \eqref{4.8} \\
&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ e^{-(1/3) \pi i} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} e^{-(7/6) \pi i} x^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right) \right. \\
& \left. \qquad\qquad\qquad\qquad + e^{-(2/3) \pi i} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} e^{-(11/6) \pi i} x^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right) \right] \\
&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ e^{-(1/3) \pi i} e^{-(7/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(2) \Gamma(\tfrac{1}{6})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{6})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right. \\
& \qquad\qquad\qquad\qquad + \left. e^{-(2/3) \pi i} e^{-(11/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(2) \Gamma(\tfrac{5}{6})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ e^{-(2/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{-(1/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
&=\frac{8\pi}{27} \frac{\tfrac{3}{2}\Gamma(\tfrac{3}{2})\,\Gamma(\tfrac{1}{2})}{\tfrac{4}{3}\Gamma(\tfrac{4}{3})\,\tfrac{2}{3}\Gamma(\tfrac{2}{3})} \frac{\tfrac{1}{6}\Gamma(\tfrac{1}{6})\,\tfrac{5}{6}\Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ e^{-(1/2) \pi i} e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right. \\
& \qquad\qquad\qquad\qquad\qquad\qquad\qquad + \left. e^{(1/2) \pi i} e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
&=\frac{8\pi}{27} \frac{\tfrac{3}{2}\,\tfrac{1}{2}\Gamma(\tfrac{1}{2})\,\Gamma(\tfrac{1}{2})}{\tfrac{4}{3}\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\,\tfrac{2}{3}\Gamma(\tfrac{2}{3})} \frac{5}{6^2} (-i) \left[ e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) - e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
&=\frac{8\pi}{27} \frac{\tfrac{3}{2}\,\tfrac{1}{2}}{\tfrac{4}{3}\,\tfrac{1}{3}\,\tfrac{2}{3}} \frac{5}{6^2} \frac{\sin(\tfrac{1}{3}\pi)}{\sin(\tfrac{1}{2}\pi)} (-i) \left[e^{(7/6) \pi i} - e^{(11/6) \pi i}\right]\,w_3(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
&=\frac{5 \cdot 3\pi}{12^2} \frac{\sqrt{3}}{2} i\sqrt{3}\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;1-x\right) \\
&=\frac{5\pi i}{32} \,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}+\frac{3\zeta}{4}\right) \\

@@

This matches the LHS of claim~\eqref{claim 2} \textbf{(up to scaling)}, as long as we continue from above the branch cut. This is consistent \textbf{(is it?)} with our continuations of $w_5$ and $w_6$ \textbf{(name)} in the calculation.
